Material Metohds

### 2019-08-28 doc/Main_Report.rmd
updating the setupData files

---
title: "MLH1 Data Report"
author: "April Peterson"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
setwd("C:/Users/alpeterson7/Documents/MLH1repo/")
#setwd("C:/Users/April/Desktop/MLH1repo")
#load(file="data/MLH1/MLH1_data_setup.RData")
load(file="data/MLH1/MLH1_data_setup_8.15.19.RData")

#### Research Description

@@

@@

@@

@@

@@

```{r basic.numbers, echo=FALSE}

@@

@@

```{r age.hists, echo=FALSE}

#meta.data.file2 = read.csv("~./MLH1repo/data/MouseMetaData61119.csv", header = TRUE)
meta.data.file2 = read.csv("~./MLH1repo/data/Mouse_MetaData_6.12.19.csv", header = TRUE)
meta.data.file2 <- meta.data.file2[!(is.na(meta.data.file2$mouse)|meta.data.file2$mouse==""),] #375

meta.data.file2$DOB <- as.Date(meta.data.file2$DOB, format= "%m/%d/%Y")#%Y 2000, %y '18,

#make Mouse meta data work
MouseMetaData.wrkin <- meta.data.file2[,c(1,4)]
colnames(MouseMetaData.wrkin) <- c("mouse", "DOB")
MouseMetaData.wrkin <- MouseMetaData.wrkin[!(is.na(MouseMetaData.wrkin$mouse)|MouseMetaData.wrkin$mouse==""),]

#add euth date for calculating age
source("~./MLH1repo/src/CommonFunc_MLH1repo.R")
PWD.KAZ_MLH1.imprv <- add_euth_date(PWD.KAZ_MLH1.imprv)
PWD.KAZ_MLH1.imprv <- add_age(PWD.KAZ_MLH1.imprv)

source("~./MLH1repo/src/CommonFunc_MLH1repo.R")
MLH1.imprv <- add_euth_date(MLH1.imprv)
#
MLH1.imprv$euth.date2 <- MLH1.imprv$euth.date
MLH1.imprv$euth.date <- as.Date(as.character(MLH1.imprv$euth.date2), format='%d%b%y')

MLH1.imprv <- add_age(MLH1.imprv)

@@

#### Mice table

Table of the mice used and MLH1 stats.

```{r, fig.height=2, fig.width=4, echo=FALSE}
#this table is TOO big
#this table is saved in the .RData file
#use kable to make tables. warning this might not work for github Rmd.
n <- kable(AP_mouse_table)

>>>>

---
title: "MLH1 Data Report"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '5'
    toc_float: yes
  pdf_document: default
---

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
setwd("C:/Users/alpeterson7/Documents/MLH1repo/")
#setwd("C:/Users/April/Desktop/MLH1repo")
#load(file="data/MLH1/MLH1_data_setup.RData")

#load main data file
load(file="data/MLH1/MLH1_data_setup_8.15.19.RData")

load(file="data/MetaData.RData")

#load functions
source("~./MLH1repo/src/CommonFunc_MLH1repo.R")
```

## Research Description

@@

- Show basics of the current data file

@@

*Main questions*

1. Which strains do I have enough mouse specific MLH1 data for?
2. What data will go into the FINAL dataset

@@

all cell image file names are anonimized and moved into bathces of a few hundred images.

@@

# Mice

## Missing Mice

This section shows / displays / catches mice which haven't been stained or quantified yet.

@@

```{r basic.numbers, echo=FALSE, eval=FALSE}

@@

This section is meant to double check the age distributions of male mice.

```{r age.hists, echo=FALSE, eval=FALSE}

meta.data$DOB <- as.Date(meta.data$DOB, format= "%m/%d/%Y")#%Y 2000, %y '18,

#make Mouse meta data work
MouseMetaData.wrkin <- meta.data[,c(1,4)]
colnames(MouseMetaData.wrkin) <- c("mouse", "DOB")

MouseMetaData.wrkin <- MouseMetaData.wrkin[!(is.na(MouseMetaData.wrkin$mouse)|MouseMetaData.wrkin$mouse==""),]

#add euth date for calculating age

MLH1.imprv <- add_euth_date(MLH1.imprv)
#
MLH1.imprv$euth.date2 <- MLH1.imprv$euth.date
MLH1.imprv$euth.date <- as.Date(as.character(MLH1.imprv$euth.date2), format='%d%b%y')
#this is currently broken
MLH1.imprv <- add_age(MLH1.imprv)

#### Is there an age effect?

make a subetted dataset for ploting mean mouse (quality < 5) MLH1 count and age.  Mice with enough ages:
WSB, KAZ, LEW, G, Cast, SPIC, MSM, MOLF, CZECH

```{r}
#run a age effect linear regression!

male.data <- AP_mouse_table_w.Ages[AP_mouse_table_w.Ages$sex.y == "male",]

lm.me  <- lm(male.data$mean_co ~ male.data$age.weeks+male.data$strain.x)

summary(lm.me)

```{r age.effect.plot}

#make sure the right dataset 
male.data <- AP_mouse_table_w.Ages[(AP_mouse_table_w.Ages$sex.y == "male") & (AP_mouse_table_w.Ages$category.y != "other"),]

male.data <- male.data[male.data$Ncells > 10,]

male.data <- add_subsp(male.data)

age.effect.plot <- ggplot(male.data, aes(y=mean_co, x=age.weeks, color=strain.y))+geom_point()+ ylim(c(15,39))+
  geom_smooth(method='lm',alpha=0.1, size=0, span=0.5 )+ggtitle("Age Effect on CO mean")+facet_wrap(~subsp.y)

#todo add line to strain.y

Given this plot it seems that there isn't a age effect. I should double check some of these mice

@@

` r knitr_exit()`

@@

### 2019-08-28 doc/MatMeth.Rmd
updating the setupData files

---
title: "Material Metohds"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_depth: '3'
    toc_float: yes
---

@@

@@

1.	Basic quality criteria,
2.	2. Manual quant pipeline for MLH1,,
3.	3. Quanti pipeline for DMC1 (not completely finished)

@@

>>>>

---
title: "Material Metohds"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_depth: '5'
    toc_float: yes
---

@@

X mice used

@@

1.	Basic quality criteria,
2.	Manual quant pipeline for MLH1 (anonimized)
3.	Quanti pipeline for DMC1 (not completely finished)

For MLH1 pachytene characterization, Cells with a full karyotype (19 autosomes and XY for spermatocyte spreads or 20 bivalents for oocyte spreads), distinct foci, and intact bivalents were included for quantification.

@@

-done in R/ specific packages
-non-parameteric  (tests and measures for dealing with count data)
